%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Journal Article
% LaTeX Template
% Version 1.4 (15/5/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com) with extensive modifications by
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{preamble.tex}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\setlength{\droptitle}{-4\baselineskip} % Move the title up

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{Exploring Recommender Systems with Graph Convolutional Networks} % Article title
\author{%
\textsc{Frederik Valdemar Schrøder, Jens Petur Tróndarson, Mathias Møller Lybech} \\[1ex] % Your name
\normalsize Aalborg University \\ % Your institution
\normalsize \href{mailto:fschra16@student.aau.dk}{fschra16@student.aau.dk} % Your email address
\normalsize \href{mailto:jtrand16@student.aau.dk}{jtrand16@student.aau.dk} % Your email address
\normalsize \href{mailto:mlybec16@student.aau.dk}{mlybec16@student.aau.dk} % Your email address
%\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
%\textsc{Jane Smith}\thanks{Corresponding author} \\[1ex] % Second author's name
%\normalsize University of Utah \\ % Second author's institution
%\normalsize \href{mailto:jane@smith.com}{jane@smith.com} % Second author's email address
}
\date{\today} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{%
\begin{abstract}
\noindent  
Graph Convolutional Network (GCN) is a state-of-the-art method for collaborative filtering (CF).
Throughout this paper we focus on two new methods for CF: LightGCN and Price-aware Recommendation with Graph Convolutional Networks (PUP).
LightGCN is inspired from Neural Graph collaborative Filtering (NGCF), and is a recommender system that only takes the node ID of items and users into account.
PUP also utilize CF, but takes prices and categories into account. 
We take a closer look at the main differences between LightGCN, NGCF and PUP.
After we have found the main differences between these, we extend LightGCN and NGCF by adding prices and categories as nodes in their input graph.
Through our experiments we show that our extension was unsuccesfull in improving the performance of these methods.
In our experiments we run our extension with different hyper parameters to see what effect they have on the results.
We also compare LightGCN to some other state-of-the-art methods and show that it performs significantly better than PUP, NGCF and the other methods.
From the results of these experiments we present some reasons to why our extension performed so poorly.
We end the paper by presenting some possible hypotheses that we can continue to work on in our master thesis.
\end{abstract}
}

%----------------------------------------------------------------------------------------
\lstset{
	basicstyle=\footnotesize,
	numbers=left, 
	numberstyle=\tiny, 
	framexleftmargin=0pt,
	breaklines=true,
	tabsize=2
}

\begin{document}

% Print the title
\maketitle

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\input{article-structure.tex}
\printbibliography[heading=bibintoc]
\label{bib:mybiblio}
%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------


%\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template
%
%  \bibitem[Figueredo and Wolf, 2009]{Figueredo:2009dg}
%  Figueredo, A.~J. and Wolf, P. S.~A. (2009).
%  \newblock Assortative pairing and life history strategy - a cross-cultural
%  study.
%  \newblock {\em Human Nature}, 20:317--330.

%\end{thebibliography}

%----------------------------------------------------------------------------------------

\end{document}
